\section{Challenges}
\label{sec:challenges}

Of course, several challenges need to be addressed when implementing such a dashboard. The most important challenges are: the availability of data, privacy concerns, and effectiveness.

\subsection{Availability of Data}

When implementing such a dashboard, one of the key issues is the availability of data. Which kinds of data are available and from what sources is highly dependent on the institution. As discussed in Section \ref{sec:data}, in the case of the University of Bamberg, several sources of data would need to be combined to create a comprehensive dashboard, and it is not clear that all data is already readily available.

Especially for the planning aspects, it is important to have data about all courses and degree programs available. Usually, degree program specifications are handed out as PDFs, which are not easily machine-readable. This data would need to be converted into a machine-readable format to be used in a dashboard. The system would also need to handle changes to degree programs, which might apply to every student (because some courses are no longer offered) or only to new students (because the degree program has been adapted).
Some universities also offer degree programs in cooperation with other universities, which would make the data gathering even more complex \cite{Dashboard-StudentProgress}.

\subsection{Privacy Concerns}
There are multiple ways in which privacy and data protection concerns could arise. For example, if the dashboard is used to suggest interventions in case of problems, it is important to ensure that the data is only accessible to the student and the responsible staff members.
In general, it is important to ensure that the data is only accessible to the people who need it and that the data is not misused. Students should be allowed to decide who can see their data and should be able to revoke access at any time. This is especially important when the data is used to suggest interventions, as this could be seen as an intrusion into the private life of the student.

Especially visualizations in which the student is compared to others are a sensitive topic. The data shown to the student must not allow for the identification of other students. For small courses, this might make it impossible to show certain visualizations, as another student would be easily identifiable.
Therefore, comparative visualizations need to strike a balance between showing useful information and protecting the privacy of the students. This is especially important when students are compared to cohorts instead of the entire student body, which, as discussed previously, might improve the information that can be gained from the visualization but will also decreas the anonymity set.

\subsection{Effectiveness}

The most important challenge is to ensure that the visualizations are actually effective. This means that the dashboard should help students to succeed in their academic career. One very important thing to consider is motivation of students.
If the visualizations are too negative, students might be tempted to give up. For example, if a student is shown that they are behind the average of their cohort, with a small chance of passing the exam, they might become demotivated and drop the class instead of making an effort and working harder.
On the other hand, if they know that they are ahead of the average, they might become complacent and work less, thus actually decreasing their chance of success.
Therefore, it is very important to conduct field tests to ensure that the visualizations are not demotivating students.

If the dashboard is used to suggest interventions or to urge students to work more, it is important to ensure that such feedback comes at the right time. Early in the semester, students will still have enough time to change their work habits and catch up, while later in the semester, it might be too late to make a difference.
On the other hand, there might not be enough data that soon to verify, whether any changes are needed at all.
Therefore, it is important to ensure that the feedback is timely and actionable.
